---
title: "babynames post"
description: |
  Introduce yourselves and play with baby names data 
author:
  - name: Billie Eilish
    url: https://example.com
  - name: Taylor Swift
    url: https://example.com
  - name: Britney Spears
    url: https://example.com
date: 11-30-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introductions

Insert a short paragraph here about each of the members of your group. You can edit the templates below. If you want italics use *one asterisk*. For bond, use **two asterisks**. You can get levels of heading with hash

# BIG HEADING
## SMALLER HEADING
### EVEN SMALLER HEADING

You can get bullet points using dash...

- first important point
- second point
- and third... 



### Billie Eilish

My favourite food on campus is Guzmen & Gomez. I get to UNSW on the bus/train. When we are allowed to travel again, the first place I am going to go is Bali. 


### Taylor Swift

My favourite food on campus is Stockmarket. To get to campus, I ride my bike. When we are allowed to travel again, the first place I am going to go is Thailand. 


### Britney Spears

My favourite food on campus is Subway. I drive my car to get to UNSW campus. When we are allowed to travel again, the first place I am going to go is New Zealand. 


***

# data viz with ggplot


### load packages 

We can use the `library()` function to load the packages we need. The `tidyverse` package contains tons of useful functions for data wrangling and visualisation (including ggplot). The `ozbabynames` package contains data from birth records in Australia. 


```{r}
library(tidyverse)
library(ozbabynames)

```

### read the babynames data

```{r}
ozbabynames <- ozbabynames

glimpse(ozbabynames)

```


### define the names you want to compare

```{r}
author_names <- c("Billie", "Taylor", "Britney")

```

### whose name is most popular?? 

```{r}

ozbabynames %>%
  filter(name %in% author_names) %>%
  group_by(name, year) %>% 
  summarise(count = sum(count)) %>%
  ggplot(aes(x = year, 
             y = count,
             colour = name)) +
  geom_line() +
  theme_bw() +
 facet_wrap(~name,
             scales = "free_y") +
  theme(legend.position = "none")
```



What does the `scales = "free y"` do? What happens if you delete it? Is the plot more meaningful with "free y" or without it?


### Recreate the plot above with your names 

```{r}
your_names <- c("name1", "name2", "name3")
```

What do you need to change about the code below to make it plot your names?

```{r}
ozbabynames %>%
  filter(name %in% author_names) %>%
  group_by(name, year) %>% 
  summarise(count = sum(count)) %>%
  ggplot(aes(x = year, 
             y = count,
             colour = name)) +
  geom_line() +
  theme_bw() +
 facet_wrap(~name,
             scales = "free_y") +
  theme(legend.position = "none")
```

Do you need `scales = "free_y"`?